SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-10 docs/questioning.tex
minor changes

In this section we provide a step-by-step exploitation model to
understand the process of carrying out application attacks based on
source code injection vulnerabilities.
Figure~\ref{fig:attacks} presents the steps of different application
attacks. For every arrow there is a
corresponding tuple that includes the transition number for
every attack. For the most part, the steps are common in all attacks. This
is because they are based on similar attack vectors as we mentioned in
the previous section. Most importantly,
Figure~\ref{fig:attacks} also illustrates in which transitions
the defenses detect corresponding attacks.

@@

{\sc xss} attacks fall ino two categories, {\it non-persistent} and
{\it persistent}. Non-persistent {\sc xss} attacks take place when the
data provided by a user is used immediately by server-side scripts to
parse and display a page of results, without properly sanitizing the
request ({\sc transition}: {\sc p-xss} 8 \text{\textbar} {\sc n-xss} 3).
Thus, in a non-persistent {\sc xss} attack the injected code
is never saved on the server and immediately becomes part of the
content that is sent back to a web user.

@@

\begin{enumerate}
\item The number of times the corresponding publication has been cited.
\item Accuracy and Computational Overhead measurements.
\item The attacks that the mechanism detects.
\end{enumerate}

@@

Table~\ref{tab:comp} shows for every mechanism its corresponding
overhead. In addition, it indicates if the overhead is applied to the
server-side ({\sc s}), or the client-side ({\sc c}). In almost half of
the approaches, 16 out of 34 (47.05\%), the overhead is provided as a
percentage. while in other cases, 7 our of 34 (20.5\%), the authors
provide the time (in terms of ms) that their mechanisms add to the
normal execution time of the protecting entity. As they do not provide
the times of normal executions, it not possible to move from absolute
time measurements to percentage overheads. In 10 cases (29,4\%), the
overhead was either not available ({\sc na}) or not quantified ({\sc
  nq}). In the case of {\sc php aspis}, its authors indicate that with
their mechanism, the execution time is doubled.

>>>>

In this section we provide a step-by-step exploitation model to
understand the process of carrying out application attacks based on
source code injection vulnerabilities.
Figure~\ref{fig:attacks} presents the steps of different application
attacks. For every arrow there is a
corresponding tuple that includes the transition number for
every attack. Every number indicates the number of the
steps taken until we reach this transition.
For the most part, the steps are common in all attacks. This
is because they are based on similar attack vectors as we mentioned in
the previous section. Most importantly,
Figure~\ref{fig:attacks} illustrates in which transitions
the defenses detect corresponding attacks.

@@

{\sc xss} attacks fall ino two categories, {\it non-persistent} and
{\it persistent}. Non-persistent {\sc xss} attacks take place when the
data provided by a user is used immediately by server-side scripts to
parse and display a page of results, without properly sanitizing the
request ({\it transition}: {\sc p-xss} 7 \text{\textbar} {\sc n-xss} 2).
Thus, in a non-persistent {\sc xss} attack the injected code
is never saved on the server and immediately becomes part of the
content that is sent back to a web user.

@@

\begin{enumerate}
\item The number of times the corresponding publication has been cited.
\item Accuracy and computational overhead measurements.
\item The attacks that the mechanism detects.
\end{enumerate}

@@

Table~\ref{tab:comp} shows for every mechanism its corresponding
overhead. In addition, it indicates if the overhead is applied to the
server-side ({\sc s}), or the client-side ({\sc c}). In almost half of
the approaches, 16 out of 34 (47.05\%), the overhead is provided as a
percentage, while in other cases, 7 our of 34 (20.5\%), the authors
provide the time (in terms of ms) that their mechanisms add to the
normal execution time of the protecting entity. Note that in some
cases, the times of normal executions are not provided,
so it is not possible to move from absolute
time measurements to percentage overheads. In 10 cases (29,4\%), the
overhead was either not available ({\sc na}) or not quantified ({\sc
  nq}). In the case of {\sc php aspis}, its authors indicate that with
their mechanism, the execution time is doubled.
